Efforts to Code Calls created a Positive Impact in Reducing Toronto's Homeless Death Counts

### 2024-01-25 outputs/paper/paper.qmd
Editted sections and outputted a new pdf according to peer review

---
title: "Analysis on the Correlations between the efforts made by the Staff of Toronto's Central Intake Line and Toronto's Homeless Death Counts"
author: 
  - Sandy Yu
thanks: "Code and data are available at: https://github.com/Jingying-yu/central_intake_calls_and_homeless_death_count.git"
date: today
date-format: long
abstract: "For the City of Toronto, the physical well-being of its local homeless population has always been one of its primary focuses. Numerous social efforts, funded by the City, were made in attempts to reduce the death rate of the local homeless population. In order to visualize the magnitude of social impact enforced by the City of Toronto, analyses were performed to investigate the correlation between the efforts made by the staff of Toronto’s Central Intake Line and the monthly homeless death counts between November 2020 to June 2023 using data from OpenDataToronto. Staff efforts such as the number of calls coded, number of referral to shelter, and number of information for homelessness prevention, were documented and compared against the monthly homeless death counts. An inverse correlation is found between the number of calls coded and the homeless death count. No discernible correlations were found between coded call types of interest and the monthly homeless death counts."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

This paper investigated the magnitude of impact created by the Central Intake Line in relation to the monthly cumulative number of deaths in the homeless community. Variables of interest such as: calls coded, number of callers referred to shelter, number of callers provided with information on homelessness prevention, and homeless death count, were obtained from the Central Intake Call Wrap-Up Codes Dataset [@Central_Intake_Call] and the Deaths of People Experiencing Homelessness Dataset [@Homeless_Death_Count] stored in the OpenDataToronto portal [@OpenDataToronto]. Statistical analyses yielded a negative correlation between the number of calls coded and the homeless death count, which implies a positive impact in reducing homeless death in Toronto. Other variables, such as number of callers referred to shelter and number of callers provided with information on homelessness prevention, yielded no meaningful correlation to the homeless death count. Therefore we cannot conclude the magnitude of their contribution to the reduction of homeless death count. Further analysis on homeless death counts by demography can be conducted based on shelter data that contains demographic values.

>>>>

---
title: "Efforts to Code Calls created a Positive Impact in Reducing Toronto's Homeless Death Counts"
subtitle: "Analysis on the Correlations between the efforts made by Toronto's Central Intake Line and local Homeless Death Counts"
author: 
  - Sandy Yu
thanks: "Code and data are available at: https://github.com/Jingying-yu/central_intake_calls_and_homeless_death_count.git"
date: today
date-format: long
abstract: "For the City of Toronto, the physical well-being of its local homeless population has always been one of its primary focuses. Numerous social efforts, funded by the City, were made in attempts to reduce the death rate of the local homeless population. In order to visualize the magnitude of social impact enforced by the City of Toronto, analyses were performed to investigate the correlation between the efforts made by the staff of Toronto’s Central Intake Line and the monthly homeless death counts between November 2020 to June 2023 using data from OpenDataToronto. Staff efforts such as the number of calls coded, number of referral to shelter, and number of information for homelessness prevention, were documented and compared against the monthly homeless death counts. An inverse correlation is found between the number of calls coded and the homeless death count. No discernible correlations were found between coded call types of interest and the monthly homeless death counts."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

This paper investigated the magnitude of impact created by the Central Intake Line in relation to the monthly cumulative number of deaths in the homeless community. Variables of interest such as: calls coded, number of callers referred to shelter, number of callers provided with information on homelessness prevention, and homeless death count, were obtained from the Central Intake Call Wrap-Up Codes Dataset [@Central_Intake_Call] and the Deaths of People Experiencing Homelessness Dataset [@Homeless_Death_Count] stored in the OpenDataToronto portal [@OpenDataToronto]. Statistical analyses yielded a negative correlation between the number of calls coded and the homeless death count, which implies a positive impact in reducing homeless death in Toronto. Other variables, such as number of callers referred to shelter and number of callers provided with information on homelessness prevention, yielded no meaningful correlation to the homeless death count. Therefore we cannot conclude the magnitude of their contribution to the reduction of homeless death count. Overall, we can only conclude that the effort of Coding Calls have a positive impact on reducing homeless death in Toronto. Further analysis on homeless death counts by demography can be conducted based on shelter data that contains demographic values.
